---
title: "Data Privacy Awarness in Discussion at the Danish Folketing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{myvignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

So in this blog I going to explore and possible answer these two questions:

* Is there any increase in sentiment of the mebers of the Danish parlimanet on the topics related to
*datatilsynet*,*persondata*,*persondataloven*,*databeskyttelse* in the parlimant discussion?

* Then, which parties are more involved in the parlimant about the above topics?

So, let's get started:

## Installing the package danparcorpR

First, we need to install the *danparcorpR* pacakge. To install this package first you need to install the following package:


```{r}
#install.packages("remotes")  # install the package
library(remotes)
```

The above package makes that you can install package from the github, which is the case of the *danparcorpR* package, at the momoment. So having the *remotes* package, you can install *dancoprR* package as the follows:

Note: Since it contains a bit of large text data inside it, installation may take a few minutes (less than 5 min) so just be patient until the below installation is completed.


```{r}
#remotes::install_github("Peymankor/danparcorpR")
```


Now, the package should have been installed and it is ready to use.

## Libraries

In our analysis in this blog, we will need the following four packages. I wrote small comments in front of them what they do,  

```{r}
library(danparcorpR)        # main library of the data
library(tidytext)           # the library for text processing
library(lubridate)          # library to deal with date data
library(tidyverse)          # library for data processing and visulization
```


## data Processing

Now, since in this specific analysis we are considering to analyze the data of whole 8 years (generally I do not recommend this one since data becomes so large on the memory better use the subset of the data as much as possible, like corpus_2010)

Here, I am joining the tables towgether,

```{r}
all_8_year <- rbind(corpus_2009, corpus_2010, corpus_2011,
            corpus_2012, corpus_2013,corpus_2014,
            corpus_2015, corpus_2016)
```

Here, we are converting the data to the *tidy* data. It means, each word of the tekst column will be one row, also we are removing the Parti with *NA* (which as I wrote in github Readme are the foormand or Minister):

```{r}
corpus_tidy_text <- all_8_year %>% 
  select(Starttid, Parti, Tekst) %>%
  drop_na(Parti) %>%
  filter(Parti != "") %>% 
  as_tibble() %>%
  unnest_tokens(word, Tekst)
```

So, after doing this, what we do is group the data with half_year, word and Parti and count them,
using the *tally* function:

```{r}
tidy_text_count <- corpus_tidy_text %>% 
  group_by(half_year=round_date(Starttid, "halfyear"), word, Parti) %>% 
  tally()
```

## Usage of the Data Privacy Related Words in whole Parlimant, 2009-2017

So in the below, we are selecting the words we want to see how much they have been used over year. I selected these words as the represntative the Data Privacy, but it could be chnaged to any other combination:

*datatilsynet*,*persondata*,*data*,*persondataloven*,
*databeskyttelse*,*datasikkerhed*,*datasikkerheden*

```{r}
whole_parlimanet <- tidy_text_count %>%
  filter(word %in% c("datatilsynet","persondata","data",
                     "persondataloven","databeskyttelse",
                     "datasikkerhed", "datasikkerheden")) %>% 
  group_by(half_year) %>%   
  summarise(sum_use=sum(n))
```  
The below plot shows number of the times the above 7 words has been mentioned in parlimante discussion, every half the year:

```{r}
ggplot(whole_parlimanet, aes(half_year, sum_use)) +
  geom_point() +
  geom_smooth() 
```

## Usage of the Data Privacy Related Words in Parlimant per parti, 2009-2017

```{r}
per_parti <- tidy_text_count %>%
  filter(word %in% c("datatilsynet","persondata","data",
                     "persondataloven","databeskyttelse",
                     "datasikkerhed", "datasikkerheden")) %>% 
  group_by(half_year,Parti) %>%   
  summarise(sum_use=sum(n))
```


```{r}
ggplot(per_parti, aes(half_year, sum_use)) +
  geom_line() +
  geom_point() +
  facet_wrap(~ Parti) 
```
